---
#title: "DS_4IZ566_Project2"
output: html_document
---


## Online Shopper's Intention Analysis

### Table of Contents
- Desription
  - Dataset nature and origin
  - Basic dataset overview
  - Columns description
- Additional info + errors
  - Check for nulls
  - Problematic rows
- Exploration analysis
  - Correlation heatmap
  - Purchasing trends
  
```{r}
# Initial libraries import

library(caret)
library(gdata)
library(ggplot2)
library(corrplot)

set.seed(150)
```

```{r}
# Data Import

df <- read.csv("Data/online_shoppers_intention.csv", sep=",")
```

## Description 🔎

### Dataset nature and origin

This dataset is called Online Shopper's Intention and comes from kaggle.com website.
https://www.kaggle.com/roshansharma/online-shoppers-intention
The dataset consists of feature vectors belonging to 12,330 sessions. The dataset was formed so that each session would belong to a different user in a 1-year period to avoid any tendency to a specific campaign, special day, user profile, or period.

### Basic dataset overview
```{r}
dim(df)
str(df)
summary(df)
```

### Columns description

**Revenue:**
Target value statingwhether cosumer purchaed something or not

```{r}
plot0 <- ggplot(df, aes(x = Revenue, fill = Revenue)) + geom_bar()

plot0
```


**Administrative, Informational, Product Related:**
Types of pages visited in one session

```{r}
plot1 <- ggplot(df, aes(x=Administrative)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 
plot1

plot2 <- ggplot(df, aes(x=Informational)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 
plot2

plot3 <- ggplot(df, aes(x=ProductRelated)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 
plot3
```

**Administrative Duration, Informational Duration, Product Related Duration:**
How much time did user spend on this type of page. Sums of all pages under this type.

```{r}
# Administrative Duration
plot1 <- ggplot(df, aes(x=Administrative_Duration)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
    ylim(0,0.006)
plot1

# Informational Duration
plot2 <- ggplot(df, aes(x=Informational_Duration)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
    ylim(0,0.001)
plot2

# Product related duration
plot3 <- ggplot(df, aes(x=ProductRelated_Duration)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
    ylim(0,0.000025)
plot3
```

**Bounce Rate:**
Bounce rate is the percentage of single page visits (or web sessions). It is the percentage of visits in which a person leaves your website from the landing page without browsing any further.

```{r}
plot4 <- ggplot(df, aes(x=BounceRates)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

plot4
```

**Exit Rate:**
Indicates how often visitors exit from website after visiting any number of pages on the site.

```{r}
plot5 <- ggplot(df, aes(x=ExitRates)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

plot5
```


**Page Value:**
Page Value is the average value for a page that a user visited before landing on the goal page or completing an Ecommerce transaction (or both).

```{r}
plot6 <- ggplot(df, aes(x=PageValues)) + geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

plot6
```

**Special Day:**
Indicates closeness to a special day (e.g. Mother's Day, Valentine's Day)

```{r}
labels <- c(1, 2, 3, 4, 5)

plot7 <- ggplot(df, aes(x = SpecialDay)) + geom_bar(fill="deeppink3") 

plot7
```
```

**Operating Systems:**
Unspecified different internet operating systems

```{r}
plot8 <- ggplot(df, aes(x = OperatingSystems)) + geom_bar(fill="deeppink3")

plot8
```

**Browser:**
Unspecified different internet browsers

```{r}
plot9 <- ggplot(df, aes(x = Browser)) + geom_bar(fill="deeppink3")

plot9
```

**Region:**
Unspecified different access regions

```{r}
plot10 <- ggplot(df, aes(x = Region)) + geom_bar(fill="deeppink3")

plot10
```

**Visitor Type:**

```{r}
plot10 <-ggplot(df, aes(x="", y=VisitorType, fill=VisitorType))+
geom_bar(width = 1, stat = "identity")

pie1 <- plot10 + coord_polar("y")
pie1

```


**Traffic Type:**

```{r}
plot11 <- ggplot(df, aes(x = TrafficType)) + geom_bar(fill="deeppink3")

plot11
```
```

**Weekend:**
Indicates if session was established during the weekend or not

```{r}
plot12 <- ggplot(df, aes(x = Weekend, fill = Weekend)) + geom_bar()

plot12
```

## Additional info + errors 💥

### Check for nulls
```{R}
null_rows <- df[is.na(df$Administrative),]

paste("Number of null rows: ", nrow(null_rows))

paste0("Percentage of dataset: ", nrow(null_rows)/nrow(df))

```

### Problematic rows

```{R}
negative_duration_rows <- df$Informational_Duration < 0

cat("Problematic rows: ",sum(negative_duration_rows, na.rm = TRUE))

```


### Correlation heatmap

```{R}

# Turning dataframe into numeric vector
df$Administrative <- as.numeric(df$Administrative)
df$Administrative_Duration <- as.numeric(df$Administrative_Duration)
df$Informational <- as.numeric(df$Informational)
df$Informational_Duration <- as.numeric(df$Informational_Duration)
df$ProductRelated <- as.numeric(df$ProductRelated)
df$ProductRelated_Duration <- as.numeric(df$ProductRelated_Duration)
df$BounceRates <- as.numeric(df$BounceRates)
df$ExitRates <- as.numeric(df$ExitRates)
df$PageValues <- as.numeric(df$PageValues)
df$SpecialDay <- as.numeric(df$SpecialDay)
df$Month <- as.numeric(df$Month)
df$OperatingSystems <- as.numeric(df$OperatingSystems)
df$Browser <- as.numeric(df$Browser)
df$Region <- as.numeric(df$Region)
df$TrafficType <- as.numeric(df$TrafficType)
df$VisitorType <- as.numeric(df$VisitorType)
df$Weekend <- as.numeric(df$Weekend)
df$Revenue <- as.numeric(df$Revenue)

str(df)

```

```{R}

M <- cor(df)
corrplot(M, method="color")

```


### Purchase trends

```{r}

positions <- c("Jan", "Feb", "Mar", "April", "May", "June", "Jul", "Aug", "Sep", "Oct", "Nov")

df <- read.csv("Data/online_shoppers_intention.csv", sep=",")

p<-ggplot(data=df, aes(x=Month, fill = Month)) + geom_bar() + scale_x_discrete(limits = positions)
p

```























